---
title: "Data Science Project"
author: "Gaocha Lee, Elizabeth Cain, Maya Fernandez, and Stephanie Konadu-Acheampong "
date: "3/5/2021"
output: 
  html_document:
    keep_md: TRUE
    toc: TRUE
    toc_float: TRUE
    df_print: paged
    code_download: true
---


```{r setup, include=FALSE}
# knitr::opts_chunk$set(echo = TRUE, message = TRUE, warning = TRUE)
```


```{r libraries}
library(readr)
library(tidyverse)
library(lubridate)
library(maps)          
library(ggmap)
library(RColorBrewer)  # for color palettes
library(sf)            # for working with spatial data
library(leaflet)       # for highly customizable mapping
library(ggthemes)      # for more themes (including theme_map())
library(plotly)        # for the ggplotly() - basic interactivity
library(gganimate)     # for adding animation layers to ggplots
library(transformr)
library(ggimage)
theme_set(theme_minimal())
```

```{r}
dataset <- read_csv("Data.csv")
View(dataset)
```

```{r}
newdataest
```
With the pandemic, students are forced to quarantine at home which results in less face-to-face interactions and more time on social media (if it's available to them). In the graph below, we used the data set to see if there is a strong relationship between the time spent on social media per day and whether or not they feel connected to their loved ones. Interestingly, the plot shows that with every age group, individuals who felt they had a connection with loved ones definitely spend more time on social media. This demonstrates that at times like these, we tend to rely on our social media platforms for social interaction. 

```{r}
newdataest$AgeCat = cut(newdataest$Age, c(0,13,18,23,33,45,60))

newdataest %>% 
  select(AgeCat, SocialMedia, Connection) %>% 
  group_by(AgeCat, Connection) %>% 
  summarize(Time_on_sm = sum(SocialMedia)) %>% 
  ggplot(aes(x = AgeCat, y = Time_on_sm,
             fill = Connection)) +
  geom_col(position = "dodge") +
  labs(title = "Hours Spent On Social Media and Connection With Loved Ones",
       x = "Age Group",
       y = "")
  
```

