---
title: "Data Science Project"
author: "Gaocha Lee, Elizabeth Cain, Maya Fernandez, and Stephanie Konadu-Acheampong "
date: "3/5/2021"
output: 
  html_document:
    keep_md: TRUE
    toc: TRUE
    toc_float: TRUE
    df_print: paged
    code_download: true
---


```{r setup, include=FALSE}
# knitr::opts_chunk$set(echo = TRUE, message = TRUE, warning = TRUE)
```


```{r libraries}
library(readr)
library(tidyverse)
library(lubridate)
library(maps)          
library(ggmap)
library(RColorBrewer)  # for color palettes
library(sf)            # for working with spatial data
library(leaflet)       # for highly customizable mapping
library(ggthemes)      # for more themes (including theme_map())
library(plotly)        # for the ggplotly() - basic interactivity
library(gganimate)     # for adding animation layers to ggplots
library(transformr)
library(ggimage)
theme_set(theme_minimal())
```

```{r}
dataset <- read_csv("Data.csv")
View(dataset)
```

```{r}
newdataest
```
With the pandemic, students are forced to quarantine at home which results in less face-to-face interactions and more time on social media (if it's accessible to them). In the graph below, we used the data set to see if there is a strong relationship between the average time spent on social media per day and whether or not they feel connected to their loved ones. Interestingly, the plot shows that between the different age groups, the results vary, and the average time spent on social media does not exactly determine whether or not there is a connection with loved ones. This can demonstrate that the connections made with loved ones do not merely come from social media interactions, nor are they a result of having to stay home with loved ones everyday. Indeed, that connection can be a result of anything depending on the individual. 



```{r}
newdataest$AgeCat = cut(newdataest$Age, c(0,13,18,23,33,45,60))

newdataest %>% 
  select(AgeCat, SocialMedia, Connection) %>% 
  group_by(AgeCat, Connection) %>% 
  summarize(avg_time_sm = mean(SocialMedia)) %>% 
  ggplot(aes(x = AgeCat, y = avg_time_sm,
             fill = Connection)) +
  geom_col(position = "dodge") +
  labs(title = "Average Hours Spent On Social Media and Connection With Loved Ones",
       x = "Age Group",
       y = "")
  
```

