---
title: "Data Science Project"
author: "Gaocha Lee, Elizabeth Cain, Maya Fernandez, and Stephanie Konadu-Acheampong "
date: "3/5/2021"
output: 
  html_document:
    keep_md: TRUE
    toc: TRUE
    toc_float: TRUE
    df_print: paged
    code_download: true
---


```{r setup, include=FALSE}
# knitr::opts_chunk$set(echo = TRUE, message = TRUE, warning = TRUE)
```


```{r libraries}
library(readr)
library(tidyverse)
library(lubridate)
library(maps)          
library(ggmap)
library(RColorBrewer)  # for color palettes
library(sf)            # for working with spatial data
library(leaflet)       # for highly customizable mapping
library(ggthemes)      # for more themes (including theme_map())
library(plotly)        # for the ggplotly() - basic interactivity
library(gganimate)     # for adding animation layers to ggplots
library(transformr)
library(ggimage)
theme_set(theme_minimal())
```

```{r}
dataset <- read_csv("Data.csv")
View(dataset)
```

```{r}
newdataest
```
With the pandemic, students are forced to quarantine at home which results in less face-to-face interactions and more time on social media (if it's accessible to them). In the graph below, we used the data set to see if there is a strong relationship between the average time spent on social media per day and whether or not they feel connected to their loved ones. Interestingly, the plot shows that between the different age groups, the results vary, and the average time spent on social media does not exactly determine whether or not there is a connection with loved ones. This can demonstrate that the connections made with loved ones do not merely come from social media interactions, nor are they a result of having to stay home with loved ones everyday. Indeed, that connection can be a result of anything depending on the individual. 



```{r}

dataset %>% 
  select(AgeCat, SocialMedia, Connection) %>% 
  group_by(AgeCat, Connection) %>% 
  summarize(avg_time_sm = mean(SocialMedia)) %>% 
  ggplot(aes(x = AgeCat, y = avg_time_sm,
             fill = Connection)) +
  geom_col(position = "dodge") +
  #geom_boxplot() +
  labs(title = "Average Hours Spent On Social Media and Connection With Loved Ones Per Age Group",
       x = "",
       y = "") +
  theme(plot.title = element_text(size = 12))
  
```


Before exploring the data set, it's important to first acknowledge that there is indeed a demographic imbalance. Of the 1,182 respondents, the research paper states that 84.3% of those subjects were 7 to 22 years of age with the mean age being 20.16 years old. This bar plot visually demonstrates that most of the data comes from school-age children and teenagers. This imbalance is understandable considering that the aim of this study was to research COVID-19 implications on the education, social life, and mental health of students. However, comparing different variables across multiple age-groups gets quite complicated and can be misleading if not carefully examined.  



Just as we observed with the previous plot, the number of respondents per region of residence also differs. This plot displays that there is indeed quite a significant difference between Delhi-NCR respondents and respondents living outside of the Delhi-NCR. Although the online-survey was originally aimed at institutions within the Delhi-NCR region, a significant number of responses from outside of Delhi-NCR was received, for distance-learning regulations forced many students to move out of homes and institutions to reside elsewhere. Of the total number of respondents, 38.3% were living outside of the Delhi-NCR.



This plot compares the median number of hours spent in class by different age groups. For the sole purpose of this study, it is important to draw attention to how many hours students are spending sitting in front of a screen each day. From this plot, we can observe that respondents within the 0-13 and 13-18 age-groups spend the most time in class per day. The researchers emphasized that different variables (time spent on online class, self-study,fitness, sleep, and social media) changes with different age distributions. Average time spent in class and age-group was one of the relationships that were inversely proportional; As age-group value increases, the average number of hours spent online starts to decrease. 


